Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-08-13 paper/paper.tex
feat: more feedback

In this paper, we analyze how well Nix and NixOS can improve reproducibility of scientific software.
To this end, we study the preCICE ecosystem~\cite{preCICEv2} as an example.
preCICE is a coupling library for partitioned multiphysics simulations.
The ecosystem includes diverse legacy solvers, adapters, language bindings, and tutorials besides the coupling library itself making it a challenging and representative testcase.
We try to build the complete ecosystem using Nix and run all tutorials.
This paper is the result of a student research project and a streamlined version of its report~\cite{studentreport}. Beyond the content of this paper, the report also includes a detailed comparison of Nix to Spack and EasyBuild, and a discussion on how to use Nix on HPC systems.

\section{Background}

@@

\section{Results}

@@

\section{Discussion}

@@

The xSDK policies also requires portable installations. Several components in the preCICE ecosystem require installation into \texttt{\$HOME} or any required files to be located at specific locations. Both, the CalculiX-preCICE adapter and the SU2-preCICE adapter require the original source code to be present as they add new features on top or patch the source code.
The current solution of cloning the code at the specific location works, but it might be better to look into Git submodules. This would moreover allow pinning the version of the original code compared to only documenting it.

@@

\section{Conclusion}

>>>>

In this paper, we analyze how well Nix and NixOS can improve reproducibility of scientific software.
To this end, we study the preCICE ecosystem~\cite{preCICEv2} as an example.
preCICE is a coupling library for partitioned multiphysics simulations.
The ecosystem includes diverse legacy solvers, adapters, language bindings, and tutorials besides the coupling library itself making it a challenging and representative testcase.
We try to build the complete ecosystem using Nix and run all tutorials.
In section~\ref{sec:background} the background to Nix and preCICE is introduced, section~\ref{sec:results} presents the case study on packaging the preCICE ecosystem including its challenges and workarounds.
After this we discuss the results in section~\ref{sec:discussion}, followed by the conclusion of this paper in section~\ref{sec:conclusion}.
This paper is the result of a student research project and a streamlined version of its report~\cite{studentreport}.
Beyond the content of this paper, the report also includes a detailed comparison of Nix to Spack and EasyBuild, and a discussion on how to use Nix on HPC systems.

\section{Background}
\label{sec:background}

@@

\section{Results}
\label{sec:results}

@@

\section{Discussion}
\label{sec:discussion}

@@

The xSDK policies also requires portable installations. Several components in the preCICE ecosystem require installation into \texttt{\$HOME} or any required files to be located at specific locations.
Both, the CalculiX-preCICE adapter and the SU2-preCICE adapter require the original source code to be present as they add new features on top or patch the source code.
The current solution that these build systems require cloning the code to a specific directory works, but it might be better to look into Git submodules, as this would result in a more portable solution.
This would moreover allow pinning the version of the original code compared to only documenting it.

@@

\section{Conclusion}
\label{sec:conclusion}
